Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-14 manuscript/manuscript.tex
simulation changes
sect. 3

\subsection{Generic Mixture}

@@

\subsection{Multivariate Skew Normal Regression}

@@

>>>>

\subsection{Generic Multivariate Skew Normal Mixture}

@@

\subsection{Multivariate Skew Normal Stochastic Representation}

@@

\subsection{Representation as Matrix Skew Normal}

We note that the multivariate skew normal regression problem can be expressed more succinctly through the use of Matrix Skew Normal distributions. In particular, we define $\mathbf{Y}_{n_k \times J}$ as the response matrix with rows $\mathbf{y}_i^T$, $(i = 1,...,n_k)$, where $n_k = \sum_{i = 1}^n(Z_i = k)$ is the total number of observations belonging to class $k$ ($k = 1,...,K$).

$$\mathbf{Y}_{n_k \times J} \sim \mathcal{MATSN}_{n_k \times J}(\mathbf{M},\boldsymbol\alpha_k,\mathbf{I}_{n_k},\boldsymbol\Sigma_k)$$

$$\text{vec}(Y) = \mathbf{y}_{n_kJ \times 1} = (\mathbf{y}^T_1,...,\mathbf{y}^T_{n_k})$$
